Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-01 article.qmd
Join captions in IDE figure

Using type annotations also allows to statically check for typing errors.
For instance, `Parameter`s can be assigned either a number or a time-dependent expression.
But can also be linked to an outside variable when composing models.
As such, they cannot be used to parametrize the initial conditions of variables,
for which we have to use a `Constant` (@fig-constant).

::: {#fig-constant layout-nrow=1 layout-valign="bottom"}

::: {#fig-parameter}
![](src/ide/ide1.png)

`Constant` are assigned with `assign(..., constant=True)` and can be used to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
The IDE automatically recognizes `e` as an `Equation`,
and provides autocompletion of the variables.
:::

::: {#fig-composition layout-nrow=1 layout-valign="bottom"}
![](src/ide/ide2.png)

A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights
wrong names (`z` is not a name in `Model`)
and
mismatched types (`x` is `Variable` and `a` must be a number or a `Constant`)
:::

Screenshots of Visual Studio Code showing tooltips and highlighted type errors.
:::

>>>>

Using type annotations also allows to statically check for typing errors.
For instance, `Parameter`s can be assigned either a number or a time-dependent expression.
But can also be linked to an outside variable when composing models.
As such, they cannot be used to parametrize the initial conditions of variables,
for which we have to use a `Constant` (@fig-ide).

::: {#fig-ide layout-ncol=2 layout-valign="bottom"}
![](src/ide/ide1.png)

![](src/ide/ide2.png)

Screenshots of Visual Studio Code showing tooltips and highlighted type errors.
`Constant` are assigned with `assign(..., constant=True)` and can be used to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
The IDE automatically recognizes `e` as an `Equation`,
and provides autocompletion of the variables.
A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights
wrong names (`z` is not a name in `Model`)
and
mismatched types (`x` is `Variable` and `a` must be a number or a `Constant`)
:::
